\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-05-13 sections/discussion.tex
Add: Information about biological benchmark data in Discussion

  The current analyses make use of one fecal microbiome transplant dataset with healthy and autistic samples, three mock community datasets and several datasets generated by two synthetic interaction methods.
  The analyses presented in this study are specific to the datasets utilized, and due to the lack of a gold standard reference dataset for microbial interaction data, it is not possible to generalize these results to datasets with widely different microbiome profiles.
  Incorporating datasets from a broad spectrum of biomes with varying microbial distributions into \ac{micone} will likely increase the robustness and generalizability of the results from these analyses.
  Furthermore, expanding the scope of the \ac{micone} pipeline to also include metagenomics sequencing data will enable an even broader access to a diverse range of datasets as well as domains of life that can be incorporated into the analysis.

>>>>

  The current analyses make use of one fecal microbiome transplant dataset with healthy and autistic samples, three mock community datasets and several datasets generated by two synthetic interaction methods.
  The analyses presented in this study are specific to the datasets utilized, and due to the lack of a gold standard reference dataset for microbial interaction data, it is not possible to generalize these results to datasets with widely different microbiome profiles.
  Incorporating datasets from a broad spectrum of biomes with varying microbial distributions into \ac{micone} will likely increase the robustness and generalizability of the results from these analyses.
  Additionally, the utilization of literature-based interactions~\cite{lima-mendezDeterminantsCommunityStructure2015a} or biological benchmark interaction data~\cite{sungGlobalMetabolicInteraction2017a} as additional sources for benchmarking
  Furthermore, expanding the scope of the \ac{micone} pipeline to also include metagenomics sequencing data will enable an even broader access to a diverse range of datasets as well as domains of life that can be incorporated into the analysis.

### 2022-05-13 sections/results.tex
Add: Information about biological benchmark data in Discussion

  Figure~\ref{fig:figure7}A show the default network compared against networks generated by altering one of the steps of the pipeline from the default.
  This result suggests that the most significant changes (many new nodes and edges are added) occur when the \ac{ta} step, \ac{op} step and the \ac{ni} step are changed.
  However, the L1 distance of networks generated by altering one of the steps of the pipeline from the default against the default network (Figure~\ref{fig:figure7}B) shows that the biggest deviations from the default network occur when the \ac{ni} step is changed.
  These results indicate that the biggest rewiring in networks occur when the network inference algorithm is changed and that the changes in the others steps do not create as significant of a difference.
  % TODO: Show proof??
  The change of taxonomy database and the filtering in the \ac{OP} step when turned off also adds a large number of new nodes, but the edges between the common nodes (with the default network) are fairly conserved.

>>>>

  Figure~\ref{fig:figure7}A show the default network compared against networks generated by altering one of the steps of the pipeline from the default.
  This result suggests that the most significant changes (many new nodes and edges are added) occur when the \ac{ta} step, \ac{op} step and the \ac{ni} step are changed.
  However, the L1 distance of networks generated by altering one of the steps of the pipeline from the default against the default network (Figure~\ref{fig:figure7}B) shows that the biggest deviations from the default network occur when the \ac{ni} step is changed.
  These results indicate that the biggest rewiring in networks occur when the network inference algorithm is changed and that the changes in the others steps do not create as significant of a difference.
  % TODO: Show proof??
  The change of taxonomy database and the filtering in the \ac{op} step when turned off also adds a large number of new nodes, but the edges between the common nodes (with the default network) are fairly conserved.
